Adolescent well-being in the digital age

### 2022-05-04 00-describe.Rmd
More informative ITU summary

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome) %>% 
  kbl(caption = "Observations per outcome") %>% 
  kable_custom()

```

@@

```{r}
tmp <- itu %>% 
  select(region, country, year, internet, mobile)
tmp %>% 
  drop_na(mobile)
```

>>>>

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome) %>% 
  kbl(caption = "Observations per outcome") %>% 
  kable_custom()
```

@@

```{r}
itu %>% 
  summarise(
    internet = sum(!is.na(internet)),
    mobile = sum(!is.na(mobile))
  )
```
